Food-web structure, stochasticity and response diversity drive temporal stability in complex communities

### 2023-10-16 _targets.Rmd
Update manuscript figures and SEM results

@@

@@

@@

          encaps_get_slope_change(
            param_list = param,
            coeff_data = coeff,
            slope_term = "richness",
            default_variable_values = c(
              "rho" = 0,
              "env_stoch" = .1,
              "ct_alive" = .2,
              "avg_int_strength" = .01,
              "h" = 2,
              "w_avg_tlvl" = 1.5,
              "Z" = 100
            )
          )
        }
        )
    ) %>%
    select(-fix_effect, -values)
  ),
  tar_target(pred_stab_comp_rho_tbl,
  pred_stab_comp_rho %>%
  select(-variable) %>%
  mutate(slope = map(slope,
      ~pivot_longer(.x,
        -c(rho, slope),
        names_to = "variable",
        values_to = "variable_values"
      )
    )
  ) %>%
  unnest(cols = slope)

  )
)
```

@@

```{r}
tar_load(pred_stab_comp_rho_tbl)
p_pred_stab_comp_rho <-
  pred_stab_comp_rho_tbl %>%
  mutate(
    response = var_replacement()[response],
    variable = var_replacement()[variable],
    ) %>%
  ggplot(aes(x = rho, y = variable_values, fill = slope)) +
  geom_raster() +
  facet_grid(cols = vars(response), rows = vars(variable), scales = "free") +
  coord_cartesian(expand = FALSE) +
  scale_fill_gradient2(
    low = "red",
    mid = "white",
    high = "blue",
    midpoint = 0,
    space = "Lab",
    na.value = "grey50",
    guide = "colourbar",
    aesthetics = "fill") +
  labs(
    x = "Environmental correlation",
    y = "Food-web structure",
    fill = "Slope Stability-Richness"
    ) +
  theme_bw() +
  theme(legend.position = "bottom")
ggsave_multiple(
  paste0("p_pred_stab_comp_rho", c(".png", ".pdf")),
  plot = p_pred_stab_comp_rho,
  path = here::here("report", "figures"),
  scale = 2.0,
  dpi = 400,
  width = 80,
  height = 80 * 1.1,
  units = "mm")
```

@@

```{r}
p_model_fw_stab_com <- model_fw_stab_comp_scaled_coeff %>%
  filter(response == "stab_com") %>%
  unnest(cols = c(coeff)) %>%
  rename(lower_ci = `2.5 %`, upper_ci = `97.5 %`) %>%
  rename_with(tolower) %>%
  filter(!str_detect(term, "(Intercept)")) %>%
  mutate(
    type = ifelse(str_detect(term, ":"), "interaction", "single"),
    term = str_replace_all(term, pattern)
    ) %>%
  filter(type == "interaction") %>%
  ggplot(aes(
      y = term, x = estimate,
      xmin = lower_ci, xmax = upper_ci
      )) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_pointrange() +
  labs(x = "Standardised coefficients") +
  theme_bw() +
  theme(axis.title.y = element_blank())
ggsave_multiple(
  paste0("p_model_fw_stab_com", c(".png", ".pdf")),
  plot = p_model_fw_stab_com,
  path = here::here("report", "figures"),
  scale = 1.8,
  dpi = 400,
  width = 80,
  height = 80 * 1.3,
  units = "mm")
```

@@

```{r}
tar_load(pred_sr_rho)
p_pred_sr_rho <- pred_sr_rho %>%
  mutate(variable = var_replacement()[variable]) %>%
  ggplot(aes(x = rho, y = values, fill = slope_richness)) +
  geom_raster() +
  facet_wrap(~variable, scales = "free_y") +
  coord_cartesian(expand = FALSE) +
  scale_fill_gradient2(
    low = "red",
    mid = "white",
    high = "blue",
    midpoint = 0,
    space = "Lab",
    na.value = "grey50",
    guide = "colourbar",
    aesthetics = "fill") +
  labs(
    x = "Environmental correlation",
    y = "Food-web structure",
    fill = "Slope Stability-Richness"
    ) +
  theme(legend.position = "bottom")
ggsave_multiple(
  paste0("p_pred_sr_rho", c(".png", ".pdf")),
  plot = p_pred_sr_rho,
  path = here::here("report", "figures"),
  scale = 2.2,
  dpi = 400,
  width = 88,
  height = 88 * .45,
  units = "mm")
```

```{r}
tar_load(pred_data)
pred_data %>%
  filter(
    ct_alive %in% c(.1),
    rho %in% c(0, .75),
    richness >= 1,
    Z == 10,
    h %in% c(3),
    avg_int_strength %in% c(.01, .1),
    w_avg_tlvl == 1.5
    ) %>%
  ggplot(aes(
      x = richness, y = stab_com,
      color = as.factor(resp_div),
      linetype = as.factor(avg_int_strength),
      alpha = as.factor(avg_int_strength)
      )) +
  ylim(2, 8) +
  geom_line(linewidth = 1) +
  scale_alpha_manual(values = c(1, 1), guide = "none") +
  facet_grid(cols = vars(env_stoch), labeller = label_both) +
  labs(
    x = "Species richness (Log)", y = "Community stability (Log)",
    linetype = "Avg. Interaction strength",
    color = "Response diversity"
  ) +
  theme_bw() +
  theme(legend.position = "bottom")

#pred_data$async <- predict(mod_tot_async, newdata = pred_data)
#pred_data$pop_stab <- predict(mod_tot_pop_stab, newdata = pred_data)
```

>>>>

            "env_stoch" = .3,

@@

            "w_avg_tlvl" = 2.0,

@@

  tar_target(default_variable_values_pred,
    c(
      "rho" = 0,
      "env_stoch" = .3,
      "w_avg_tlvl" = 2,
      "Z" = 100

@@

          encaps_get_slope_change(
            param_list = param,
            coeff_data = coeff,
            slope_term = "richness",
            default_variable_values = default_variable_values_pred
          )
        }
        )
    ) %>%
    select(-fix_effect, -values) %>%
    select(-variable) %>%
    mutate(slope = map(slope,
      ~pivot_longer(.x,
        -c(rho, slope),
        names_to = "variable",
        values_to = "variable_values"
      )
    )
  ) %>%
  unnest(cols = slope)
  )
)
```

@@

```{r}
tar_load(pred_stab_comp_rho)
p_pred_stab_comp_rho <-
  pred_stab_comp_rho %>%
  mutate(
    response = var_replacement()[response],
    variable = var_replacement()[variable],
    ) %>%
  ggplot(aes(x = rho, y = variable_values, fill = slope)) +
  geom_raster() +
  facet_grid(cols = vars(response), rows = vars(variable), scales = "free") +
  coord_cartesian(expand = FALSE) +
  scale_fill_gradient2(
    low = "red",
    mid = "white",
    high = "blue",
    midpoint = 0,
    space = "Lab",
    na.value = "grey50",
    guide = "colourbar",
    aesthetics = "fill") +
  labs(
    x = "Environmental correlation",
    y = "Food-web structure",
    fill = "Slope Stability-Richness"
    ) +
  theme_bw() +
  theme(legend.position = "bottom")
ggsave_multiple(
  paste0("p_pred_stab_comp_rho", c(".png", ".pdf")),
  plot = p_pred_stab_comp_rho,
  path = here::here("report", "figures"),
  scale = 2.0,
  dpi = 400,
  width = 80,
  height = 80 * 1.1,
  units = "mm")
```

@@

```{r}
p_model_fw_stab_com_int <- model_fw_stab_comp_scaled_coeff %>%
  filter(response == "stab_com") %>%
  unnest(cols = c(coeff)) %>%
  rename(lower_ci = `2.5 %`, upper_ci = `97.5 %`) %>%
  rename_with(tolower) %>%
  filter(!str_detect(term, "(Intercept)")) %>%
  mutate(
    type = ifelse(str_detect(term, ":"), "interaction", "single"),
    term = str_replace_all(term, pattern)
    ) %>%
  filter(type == "interaction") %>%
  ggplot(aes(
      y = term, x = estimate,
      xmin = lower_ci, xmax = upper_ci
      )) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_pointrange() +
  labs(x = "Standardised coefficients") +
  theme_bw() +
  theme(axis.title.y = element_blank())
ggsave_multiple(
  paste0("p_model_fw_stab_com_int", c(".png", ".pdf")),
  plot = p_model_fw_stab_com_int,
  path = here::here("report", "figures"),
  scale = 1.8,
  dpi = 400,
  width = 80,
  height = 80 * 1.3,
  units = "mm")
```

```{r}
p_model_fw_stab_com_single <- model_fw_stab_comp_scaled_coeff %>%
  filter(response == "stab_com") %>%
  unnest(cols = c(coeff)) %>%
  rename(lower_ci = `2.5 %`, upper_ci = `97.5 %`) %>%
  rename_with(tolower) %>%
  filter(!str_detect(term, "(Intercept)")) %>%
  mutate(
    type = ifelse(str_detect(term, ":"), "interaction", "single"),
    term = str_replace_all(term, pattern)
    ) %>%
  filter(type == "single") %>%
  ggplot(aes(
      y = term, x = estimate,
      xmin = lower_ci, xmax = upper_ci
      )) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_pointrange() +
  labs(x = "Standardised coefficients") +
  theme_bw() +
  theme(axis.title.y = element_blank())
p_model_fw_stab_com <- plot_grid(
  p_model_fw_stab_com_int,
  plot_grid(p_model_fw_stab_com_single, NULL, nrow = 2),
  ncol = 2,
  labels = "auto"
)
ggsave_multiple(
  paste0("p_model_fw_stab_com", c(".png", ".pdf")),
  plot = p_model_fw_stab_com,
  path = here::here("report", "figures"),
  scale = 2.4,
  dpi = 400,
  width = 80,
  height = 80 * 1,
  units = "mm")
```

@@

```{r}
tar_load(pred_stab_comp_rho)
p_pred_sr_rho <- pred_stab_comp_rho %>%
  filter(response == "stab_com") %>%
  mutate(variable = var_replacement()[variable]) %>%
  ggplot(aes(x = rho, y = variable_values, fill = slope)) +
  geom_raster() +
  facet_wrap(~variable, scales = "free_y") +
  coord_cartesian(expand = FALSE) +
  scale_fill_gradient2(
    low = "red",
    mid = "white",
    high = "blue",
    midpoint = 0,
    space = "Lab",
    na.value = "grey50",
    guide = "colourbar",
    aesthetics = "fill") +
  labs(
    x = "Environmental correlation",
    y = "Food-web structure",
    fill = "Slope Stability-Richness"
    ) +
  theme(
    legend.position = "bottom",
    legend.key.width = unit(2.5, "cm"),
    plot.margin = margin(l = 10, r = 10, unit = "pt")
  )
ggsave_multiple(
  paste0("p_pred_sr_rho", c(".png", ".pdf")),
  plot = p_pred_sr_rho,
  path = here::here("report", "figures"),
  scale = 2.2,
  dpi = 400,
  width = 120,
  height = 120 * .45,
  units = "mm")
```

```{r}
tar_load(pred_data)
p_pred_sr_rho_int_env <- pred_data %>%
  filter(
    ct_alive %in% c(.1),
    rho %in% c(0, .75),
    richness >= 1,
    Z == 100,
    h %in% c(2),
    avg_int_strength %in% c(.01, .1),
    w_avg_tlvl == 2.0
    ) %>%
  ggplot(aes(
      x = richness, y = stab_com,
      color = as.factor(rho),
      fill = as.factor(rho),
      linetype = as.factor(avg_int_strength),
      alpha = as.factor(avg_int_strength)
      )) +
  ylim(2, 8) +
  geom_line(linewidth = .8) +
  geom_ribbon(aes(ymin = stab_com - stab_com_se, ymax = stab_com + stab_com_se), alpha = .3, color = NA) +
  scale_alpha_manual(values = c(1, 1), guide = "none") +
  facet_grid(
    cols = vars(env_stoch),
    labeller = as_labeller(function(x) paste0("Environmental stochasticity: ", x))) +
  labs(
    x = "Species richness (Log)", y = "Community stability (Log)",
    linetype = "Avg. Interaction strength",
    color = "Environmental correlation", fill = "Environmental correlation"
  ) +
  theme_bw() +
  theme(legend.position = "bottom")

#pred_data$async <- predict(mod_tot_async, newdata = pred_data)
#pred_data$pop_stab <- predict(mod_tot_pop_stab, newdata = pred_data)

```
```{r}
p_pred_sr <- plot_grid(
  p_pred_sr_rho_int_env + theme(legend.position = "right"),
  p_pred_sr_rho,
  nrow = 2,
  labels = "auto"
)
ggsave_multiple(
  paste0("p_pred_sr", c(".png", ".pdf")),
  plot = p_pred_sr,
  path = here::here("report", "figures"),
  scale = 2.0,
  dpi = 400,
  width = 120,
  height = 120 * .8,
  units = "mm")
```

### 2023-10-16 paper/manuscript.Rmd
Update manuscript figures and SEM results

```{r}
sem_cap <- paste0(
  "Structural Equation Model linking initial model parameters to resulting
  temporal stability of biomass. Arrows display positive (continuous) and
  negative (dashed) standardised effects. Initial parameters were initial
  species richness, initial connectance, Prey-Predator Mass Ration (PPMR), hill
  exponent, variance of stochastic mortality rates (Env. stochasticity), and
  cross-correlation among species mortality rates (Env. correlation). We only
  displayed standardised coefficients whose absolute values are superior to 0.1
  are displayed. SEM containing containing further partition of Statistical
  Averaging Effect and Compensatory effects is displayed in Fig. SXX.")
```

@@

get_eff <- function(y = "pop_stab", x = "richness", d = 2, effect_type = "direct", tab = sem_eff_tab) {
  mask <- tab$response == y & tab$predictor == x &
    tab$effect_type == effect_type
  round(tab[mask, ]$effect, d)
}

rpt <- get_eff(y = "pop_stab", x = "w_avg_tlvl")
rph <- get_eff(y = "pop_stab", x = "h")
rpe <- get_eff(y = "pop_stab", x = "env_stoch")
rsr <- get_eff(y = "sae_even", x = "richness")
ret <- get_eff(y = "evenness_sae", x = "w_avg_tlvl")
rer <- get_eff(y = "evenness_sae", x = "richness")
rea <- get_eff(y = "evenness_sae", x = "avg_int_strength")
rec <- get_eff(y = "evenness_sae", x = "ct_alive")
reh <- get_eff(y = "evenness_sae", x = "h")

ria <- get_eff(y = "cpe_int", x = "avg_int_strength")
ric <- get_eff(y = "cpe_int", x = "ct_alive")
rih <- get_eff(y = "cpe_int", x = "h")
rir <- get_eff(y = "cpe_int", x = "richness")

rvr <- get_eff(y = "cpe_env", x = "richness")
rvo <- get_eff(y = "cpe_env", x = "rho")
```
```{r, eval = FALSE}
sem_eff_tab %>%
  filter(abs(effect) > .1, effect_type == "direct")
```

We found that food-web structure had significant effect on temporal population
stability such as average trophic level and type III functional response (i.e. h = 3)
increase population stability (resp. $r_\delta$= `r rpt` and `r rph`, $r_\delta$
being the standardized coefficient, Fig. \@ref(fig:sem)). However the strength
of environmental stochasticity had a strong negative effect on population
stability ($r_\delta$= `r rpe`).

We further found that food-web structure had a strong impact on statistical
averaging effects, which raises from independant species fluctuations weigthed
the evenness of their biomass. As expected the mathematical relationship (eq. XX),
species richness was the only driver of even statistical averaging effect
($r_\delta$= `r rsr`, Fig. \@ref(fig:sem)). Average trophic level had a strong negative effect on
evenness ($r_\delta$= `r ret`), meaning that biomass are more inequally
distributed among species, thereby downplaying the portefolio effect raised from
species richness. But richness had also a small negative effect on evenness
($r_\delta$= `r rer`). Constrastingly, connectance, average interaction
strength, and type III functional response all increased biomass evenness
(resp. $r_\delta$= `r rec`, `r rea`, and `r reh`).

Food-web structure and cross-correlation among species mortality rates had
strong effects on compensatory dynamics. Average trophic level, connectance and
type III functional response had a negative effect on compensatory effect
raising from species interaction (resp. $r_\delta$= `r ria`, `r ric`, `r rih`,
Fig. \@ref(fig:sem)) there decreasing asynchony, while richness had a positive
effect ($r_\delta$= `r rir`), there increasingasynchrony. In turn, richness and
cross-correlation among species mortality rates had a negative effect on
compensatory dynamic raising from environmental stochasticity
($r_\delta$= `r rvr` and `r rvo`).

```{r}
rscp <- get_eff(y = "stab_com", x = "pop_stab")
rsca <- get_eff(y = "stab_com", x = "async")

rav <- get_eff(y = "async", x = "cpe_env")
rae <- get_eff(y = "async", x = "evenness_sae")

rass <- get_eff(y = "async", x = "sae_even")
rasi <- get_eff(y = "async", x = "cpe_int")
```

Population stability had a positive effect twice higher than asynchrony on the
temporal stability of community (resp. $r_\delta$= `r rscp` and `r rsca`). In turn, asynchrony
was mostly driven by evenness of biomass distribution and compensatory dynamics
raising from environmental stochasticity (resp. $r_\delta$= `r rae` and `r rav`, Fig.
\@ref(fig:sem)) than from statistical averaging emerging from species richness
(i.e. even) and compensatory dynamics emerging from species interaction (resp.
$r_\delta$= `r rass` and `r rasi`).

@@

```{r}
pred_cap <- "Relationship between community stability and species richness
according to environmental stochasticity and response diversity. (a) Simulation [add parameters selected], (b) Prediction from the linear model. "
```

```{r pred, fig.cap = pred_cap}
knitr::include_graphics(here("report", "figures", "p_sim_pred.pdf"))
```

Using a more complex linear model (i.e. containing interaction), we investigated more
in detail the relationship between community stability and species richness and
how this relation is affected by environmental stochasticity and cross
correlation among species mortality rates. We found that environmental
stochasticity decrease overall community stability but does not change the shape
of the community stability-species richness relationship (put some numbers, Fig.
\@ref(fig:pred)a and b). In contrasts, cross correlation among species mortality rates
both decreases overall community stability and nullifies the community
stability-species richness relationship. Surpringly, we found that
despite average interaction strength has a small overall effect on
community stability, high average interaction strength change the shape of the
community stability-species richness relationship from positive to negative when
response diversity is low (put some numbers, Fig. \@ref(fig:pred)b).

>>>>

```{r}
sem_cap <- paste0(
  "Structural Equation Model linking initial model parameters to resulting
  temporal stability of biomass. Arrows display positive (continuous) and
  negative (dashed) standardised effects. Initial parameters were initial
  species richness, initial connectance, Prey-Predator Mass Ratio (PPMR), hill
  exponent, variance of stochastic mortality rates (Env. stochasticity), and
  cross-correlation among species mortality rates (Env. correlation). We only
  displayed standardised coefficients whose absolute values are superior to 0.1
  are displayed. SEM containing containing further partition of Statistical
  Averaging Effect and Compensatory effects is displayed in Fig. SXX.")
```

@@

get_eff <- function(
  y = "pop_stab", x = "richness",
  d = 2, effect_type = "direct",
  tab = sem_simplified_eff_tab) {
  mask <- tab$response == y & tab$predictor == x &
    tab$effect_type == effect_type
  round(tab[mask, ]$effect, d)
}

rpt <- get_eff(y = "pop_stab", x = "w_avg_tlvl")
rph <- get_eff(y = "pop_stab", x = "h")
rpe <- get_eff(y = "pop_stab", x = "env_stoch")

rsr <- get_eff(y = "sae_total", x = "richness")
rst <- get_eff(y = "sae_total", x = "w_avg_tlvl")
rsi <- get_eff(y = "sae_total", x = "avg_int_strength")
rsc <- get_eff(y = "sae_total", x = "ct_alive")

rcr <- get_eff(y = "cpe", x = "richness")
rci <- get_eff(y = "cpe", x = "avg_int_strength")
rco <- get_eff(y = "cpe", x = "rho")

# Detailled SEM coefficients
rsr <- get_eff(y = "sae_even", x = "richness", tab = sem_eff_tab)
ret <- get_eff(y = "evenness_sae", x = "w_avg_tlvl", tab = sem_eff_tab)
rer <- get_eff(y = "evenness_sae", x = "richness", tab = sem_eff_tab)
rea <- get_eff(y = "evenness_sae", x = "avg_int_strength", tab = sem_eff_tab)
rec <- get_eff(y = "evenness_sae", x = "ct_alive", tab = sem_eff_tab)
reh <- get_eff(y = "evenness_sae", x = "h", tab = sem_eff_tab)

ria <- get_eff(y = "cpe_int", x = "avg_int_strength", tab = sem_eff_tab)
ric <- get_eff(y = "cpe_int", x = "ct_alive", tab = sem_eff_tab)
rih <- get_eff(y = "cpe_int", x = "h", tab = sem_eff_tab)
rir <- get_eff(y = "cpe_int", x = "richness", tab = sem_eff_tab)

rvr <- get_eff(y = "cpe_env", x = "richness", tab = sem_eff_tab)
rvo <- get_eff(y = "cpe_env", x = "rho", tab = sem_eff_tab)
```
```{r, eval = FALSE}
sem_simplified_eff_tab %>%
  filter(abs(effect) > .1, effect_type == "direct")
```

We found that food-web structure had significant effect on temporal population
stability such as average trophic level and type III functional response (i.e. hill exponent = 3)
increase population stability (resp. $r_\delta$= `r rpt` and `r rph`, $r_\delta$
being the standardized coefficient, Fig. \@ref(fig:sem)). However the strength
of environmental stochasticity had a strong negative effect on population
stability ($r_\delta$= `r rpe`).

We further found that food-web structure had a strong impact on statistical
averaging effects, which raises from independant species fluctuations weigthed
the evenness of their biomass. As expected the mathematical relationship (eq.
XX), species richness was a main positive driver of statistical averaging effect
($r_\delta$= `r rsr`, Fig. \@ref(fig:sem)), thereby increasing asynchrony.
Average trophic level and average interaction strength had strong negative
effects on statistical averaging effects (resp. $r_\delta$= `r rst` and
`r rsi`), thereby downplaying the portefolio effect raised from species
richness. In turn, we found that average interaction strength had a small
positive effect on compensatory dynamics ($r_\delta$= `r rci`, Fig.
\@ref(fig:sem)). Cross-correlation among species mortality rates had a
strong negative effect on compensatory dynamics ($r_\delta$= `r rco`), meaning
that the loss of response diversity result in a strong decrease in compensatory
dynamics.

```{r}

rscp <- get_eff(y = "stab_com", x = "pop_stab", tab = sem_eff_tab)
rsca <- get_eff(y = "stab_com", x = "async", tab = sem_eff_tab)

rac <- get_eff(y = "async", x = "cpe")
ras <- get_eff(y = "async", x = "sae_total")

#
rav <- get_eff(y = "async", x = "cpe_env", tab = sem_eff_tab)
rae <- get_eff(y = "async", x = "evenness_sae", tab = sem_eff_tab)

rass <- get_eff(y = "async", x = "sae_even", tab = sem_eff_tab)
rasi <- get_eff(y = "async", x = "cpe_int", tab = sem_eff_tab)
```

Population stability had a positive effect twice higher than asynchrony on the
temporal stability of community (resp. $r_\delta$= `r rscp` and `r rsca`). In
turn, asynchrony was equally driven by statistical averaging effects and
compensatory dynamics (resp.
$r_\delta$= `r rac` and `r ras`, Fig. \@ref(fig:sem)).

@@

```{r}
tar_load(default_variable_values_pred)
pv <- default_variable_values_pred
pv_cap <- paste0(
  "connectance = ", pv["ct_alive"],
  ", average interaction strength = ", pv["avg_int_strength"],
  ", average trophic level = ", pv["w_avg_tlvl"],
  ", hill exponent = ", pv["h"],
  ", Predator-Prey Mass Ration = ", pv["Z"],
  ", environmental correlation = ", pv["rho"],
  ", and environmental stochasticity = ", pv["env_stoch"]

)
pred_cap <- paste0("Prediction of the statistical model linking the temporal stability
  of community biomass and species richness. Default parameter values: ", pv_cap, ".") %>%
  str_replace_all("\\s+", " ")
```

```{r pred, fig.cap = pred_cap}
knitr::include_graphics(here("report", "figures", "p_pred_sr.pdf"))
```

Using a more complex linear model (i.e. including interactions), we investigated more
in detail the relationship between community stability and species richness and
how this relation is affected by environmental stochasticity and cross
correlation among species mortality rates. We found that environmental
stochasticity decrease overall community stability but has only little effect on
the shape of the community stability-species richness relationship (put some
numbers, Fig. \@ref(fig:pred)a and b). In contrasts, cross correlation among
species mortality rates both decreases overall community stability and nullifies
the community stability-species richness relationship. Surpringly, we found that
despite average interaction strength has a small overall effect on
community stability, high average interaction strength change the shape of the
community stability-species richness relationship from positive to negative when
response diversity is low (put some numbers, Fig. \@ref(fig:pred)b).
